%%%%%
%%
%% This file sets up the Abil datatype and creates Abil macros.  These
%% are for abilities that characters may have.
%%
%%%%%

\DECLARESUBTYPE{Abil}{Element}
\PRESETS{Abil}{
  \F\MYtext	%% text of ability, read by user
  \F\MYeffect	%% effect text of ability, read by recipient(s)
  }


%%%%%
%% \ability{<name>}{<text>}{<effect>}
%%
%% \ability is a wrapper around \INSTANCE, useful for 1-shot abilities,
%% etc.
\newinstance{Abil}{\ability[3]}{
  \s\MYname{#1}\s\MYtext{#2}\s\MYeffect{#3}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\NEW{Abil}{\swordsa}{
  \s\MYname	{Proficiency: Swords I}
  \s\MYtext	{You can use basic swords}
  \s\MYeffect	{I can use swords}
  }

\NEW{Abil}{\swordsb}{
  \s\MYname	{Proficiency: Swords II}
  \s\MYtext	{You can use advanced swords. Cannot be taken without Proficiency: Swords I.}
  \s\MYeffect	{I can use advanced swords}
  }

\NEW{Abil}{\axea}{
  \s\MYname	{Proficiency: Axes I}
  \s\MYtext	{You can use basic axes}
  \s\MYeffect	{I can use axes}
  }

\NEW{Abil}{\axeb}{
  \s\MYname	{Proficiency: Axes II}
  \s\MYtext	{You can use advanced axes. Cannot be taken without Proficiency: Axes I.}
  \s\MYeffect	{I can use advanced axes}
  }

\NEW{Abil}{\rangeda}{
  \s\MYname	{Proficiency: Ranged I}
  \s\MYtext	{You can use basic ranged weapons}
  \s\MYeffect	{I can use ranged weapons}
  }

\NEW{Abil}{\rangedb}{
  \s\MYname	{Proficiency: Ranged II}
  \s\MYtext	{You can use advanced ranged weapons. Cannot be taken without Proficiency: Ranged I.}
  \s\MYeffect	{I can use advanced ranged weapons}
  }

\NEW{Abil}{\throwa}{
  \s\MYname	{Proficiency: Thrown I}
  \s\MYtext	{You can use basic throwing weapons}
  \s\MYeffect	{I can use throwing weapons}
  }

\NEW{Abil}{\throwb}{
  \s\MYname	{Proficiency: Thrown II}
  \s\MYtext	{You can use advanced throwing weapons. Cannot be taken without Proficiency: Thrown I.}
  \s\MYeffect	{I can use advanced throwing weapons}
  }

\NEW{Abil}{\firea}{
  \s\MYname	{Proficiency: Fire I}
  \s\MYtext	{You can cast basic fire spells}
  \s\MYeffect	{I can use fire spells}
  }

\NEW{Abil}{\fireb}{
  \s\MYname	{Proficiency: Fire II}
  \s\MYtext	{You can cast advanced fire spells. Cannot be taken without Proficiency: Fire I.}
  \s\MYeffect	{I can use advanced fire spells}
  }

\NEW{Abil}{\lightninga}{
  \s\MYname	{Proficiency: Lightning I}
  \s\MYtext	{You can cast basic lightning spells}
  \s\MYeffect	{I can use lightning spells}
  }

\NEW{Abil}{\lightningb}{
  \s\MYname	{Proficiency: Lightning II}
  \s\MYtext	{You can cast advanced lightning spells. Cannot be taken without Proficiency: Lightning I.}
  \s\MYeffect	{I can use advanced lightning spells}
  }

\NEW{Abil}{\eartha}{
  \s\MYname	{Proficiency: Earth I}
  \s\MYtext	{You can cast basic earth spells}
  \s\MYeffect	{I can use earth spells}
  }

\NEW{Abil}{\earhtb}{
  \s\MYname	{Proficiency: Earth II}
  \s\MYtext	{You can cast advanced earth spells. Cannot be taken without Proficiency: Earth I.}
  \s\MYeffect	{I can use advanced earth spells}
  }

\NEW{Abil}{\armor}{
  \s\MYname	{Proficiency: Armor}
  \s\MYtext	{You can use advanced armor}
  \s\MYeffect	{I can use advanced armor}
  }

\NEW{Abil}{\axeDam}{
  \s\MYname	{Axe Damage}
  \s\MYtext	{All attacks with an axe that you make deal 1 additional damage.}
  \s\MYeffect	{I am good with axes.}
  }

\NEW{Abil}{\swordSpeed}{
  \s\MYname	{Sword Speed}
  \s\MYtext	{Reduce the cooldown for any attack with a sword you make by 1.}
  \s\MYeffect	{I am good with swords.}
  }

\NEW{Abil}{\sack}{
  \s\MYname	{Sack}
  \s\MYtext	{You have a sack to carry items (ask a GM for the physrep).}
  \s\MYeffect	{I'm good at looting things.}
  }

\NEW{Abil}{\hp}{
  \s\MYname	{Endurance}
  \s\MYtext	{Increase you maximum HP by 2. You may take this more than once.}
  \s\MYeffect	{I am hard to kill.}
  }

\NEW{Abil}{\levitate}{
  \s\MYname	{Levitation}
  \s\MYtext	{Ignore the effects of any pit that you step in.}
  \s\MYeffect	{I can fly.}
  }

\NEW{Abil}{\hpTransfer}{
  \s\MYname	{Lay on Hands}
  \s\MYtext	{On a 3-count you may give one hit point to an ally at the cost of two hit points of damage to yourself. This can not put another player at more than their starting hit points.}
  \s\MYeffect	{I heal you.}
  }

%\NEW{Abil}{\lucid}{
%  \s\MYname	{Lucid}
%  \s\MYtext	{You may still hold a torch, speak and drink potions while dazed.}
%  \s\MYeffect	{I can act while dazed.}
%  }

\NEW{Abil}{\mem}{
  \s\MYname	{Extended Memory}
  \s\MYtext	{You may now wait as long as you like between performing the ritual for a spell and throwing the corresponding spell packet. However, beginning the ritual for any spell negates any progress on the cooldown of any other spells that you have.}
  \s\MYeffect	{I have a good memory.}
  }

\NEW{Abil}{\daze}{
  \s\MYname	{Dazing blow}
  \s\MYtext	{One per 30 seconds you can make an attack with a club or fists for {\bf slow} instead of its normal damage.}
  \s\MYeffect	{I can stun people with my club attacks.}
  }

\NEW{Abil}{\alchemy}{
  \s\MYname	{Alchemy}
  \s\MYtext	{When consuming a potion you can get any of the possible potion effects of your choice rather than the one standard to that type of potion.}
  \s\MYeffect	{I can transmute potions.}
  }

\NEW{Abil}{\push}{
  \s\MYname	{Forcing blow}
  \s\MYtext	{You may add push to the incant of any melee attack.}
  \s\MYeffect	{My attacks force you back.}
  }

\NEW{Abil}{\fireres}{
  \s\MYname	{Fire Resistance}
  \s\MYtext	{You are immune to fire damage.}
  \s\MYeffect	{I am immune to fire.}
  }

\NEW{Abil}{\lightres}{
  \s\MYname	{Lightning Resistance}
  \s\MYtext	{You are immune to lightning damage.}
  \s\MYeffect	{I am immune to lightning.}
  }

\NEW{Abil}{\poires}{
  \s\MYname	{Poison Resistance}
  \s\MYtext	{You are immune to poison damage.}
  \s\MYeffect	{I am immune to poison.}
  }

\NEW{Abil}{\freedomofmovement}{
  \s\MYname	{Freedom of Movement}
  \s\MYtext	{You are immune to the effects of root and slow.}
  \s\MYeffect	{I can move freely.}
  }

\NEW{Abil}{\ammo}{
  \s\MYname	{Extra Ammunition}
  \s\MYtext	{You may have one additional piece of ammunition for ranged weapons (ask a GM for the physrep)}
  \s\MYeffect	{I have extra ammo.}
  }

\NEW{Abil}{\guard}{
  \s\MYname	{Guard}
  \s\MYtext	{Once a minute, you may enter guard mode for up to 30 seconds. While in guard mode you may not make use of any mechanics, but are immune to all attacks.}
  \s\MYeffect	{Stand behind me!}
  }

\NEW{Abil}{\dodge}{
  \s\MYname	{Nimble}
  \s\MYtext	{Once every five minutes you may dodge an attack of your choice.}
  \s\MYeffect	{You can't hit me.}
  }

\NEW{Abil}{\extraheal}{
  \s\MYname	{Health Nut}
  \s\MYtext	{You heal twice as many hit points when you consume a health potion.}
  \s\MYeffect	{I like health potions.}
  }

\NEW{Abil}{\extraspeed}{
  \s\MYname	{Speed Nut}
  \s\MYtext	{You may take twice as many free attacks when you consume a speed potion.}
  \s\MYeffect	{I like speed potions.}
  }

\NEW{Abil}{\juggle}{
  \s\MYname {Juggling}
  \s\MYtest {You may perform the cooldown mechanics for multiple thrown weapons simultaneously. If more than one is not in the air for five seconds consecutively, its cooldown is reset.}
  \s\MYeffect {I can juggle several throwing weapons.}
  }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
