\documentclass[green]{grimrock}
\begin{document}
\name{\gRules{}}

\section{Scenario}

A dungeon entrance lies at the top of Mount Grimrock, inaccessible except by airship.  Prisoner committing egregious crimes against the crown are sentenced to be thrown into the dungeon of Grimrock and abandoned there.  Any who pass through the dungeon and return are pardoned for their crimes, but no one has ever returned.

You and three other criminals have been chained together and banished into the dungeons of Grimrock.


\section{Chain}

All of the players are chained together. The manacles and chain will be represented by clipping players onto a loop of rope.  In principle the players are manacled together and cannot free themselves from the rope, but in practice players may need to detach for safety reasons or to rearrange the party.

If any player is detached from the chain, all players attached to the chain are {\bf rooted}.  Any players unattached are {\bf dazed} and may only walk towards the chain.

\section{Dungeon Components}

{\bf Pits:}  Large pits are represented by red masking tape on the floor.  If any part of your body touches the interior of a pit, you trip into it, but are caught by your teammates.  You take 1 piercing damage, and are {\bf immobile} until you escape the pit, which may only be done with the assistance of a teammate.  Pulling an ally out of a pit is a 15-count, during which time you are {\bf immobile}.

{\bf Strings:} Strings represent hazardous materials.  If you touch a string, take 1 piercing damage immediately.  There may be additional effects controlled by a GM.

{\bf Pressure Plates:} Pressure plates are represented by blue masking tape on the floor.  These plates may vary in sensitivity.

{\bf Buttons:} Buttons on the wall are represented by small signs.

{\bf Stairs:} Stairs may not be transversed unless explicitly indicated otherwise.

{\bf Crystal of Life:}  Between very floor is a Crystal of Life which will heal players fully, remove status effects, revive {\bf downed} characters, save the party progress, and grant each player a new {\bf talent}.

\section{Light}

Dungeons are dark and you will need a source of light to allow you to escape.  You have a torch, but it will only last so long.

Torches are physrepped by foam rods.  To use torches to illuminate, one player must hold it above their head at all times.  If the torch is lowered, set down, or dropped, the dungeon is cast into darkness: until they have a source of light, players may only walk heel-toe.

Once lit, a torch will remain lit for only 20 minutes, as timed by a GM.  If your last torch is exhausted, the game will end and your party will be lost in the dungeon forever.

\section{Talents}

Characters will accumulate {\bf talents} over the course of the game.  These represent additional abilities that the player will gain access to.  See the appropriate greensheet for more information.  No player may take the same talent twice.

\section{Combat}

Combat will be represented by player skill in dodging physreps.  All attacks have an incant associated with them that describes the effects, usually including an amount of damage, any possibly status effects or attack modifiers.  When you perform the attack speak the incant clearly.  If you are hit by the attack --- the attacker calls the shot in case of a tie --- take the corresponding effect.  For example, an attack with an incant "Silence 2" would cause 2 damage and inflict {\bf Silence}.  If you have DR, reduce the damage taken by that amount.

Certain attacks may be resisted or dodged.  If an attack fails to penetrate your DR or you are immune to the attack, incant ``resist''.  If you an ability to {\bf dodge} the attack, incant ``dodge''.  This represents the expenditure of a limited-use ability.


Different attacks are represented in different ways.  Most attacks have a cooldown ritual, which is performed before the implementing the attack, although for physical attacks these rituals can be done in advance.

{\bf Melee:} Melee attacks are usable while holding a melee weapon and the attack is physrepped by a ping-pong ball.  Throw the ball and speak the incant.  You must perform a cooldown ritual before performing an attack.  To do so \TODO{Figure out melee cooldown}.

{\bf Thrown:}  Thrown weapons are indicated by juggling balls.  To perform a thrown attack, throw the ball \emph{underhanded}.  Thrown attacks have a cooldown ritual.  To perform the ritual, throw the juggling ball in the air and catch it a number of times equal to the cooldown number.  The ball must be thrown at least three feet in the air, and caught at or below the height it was thrown.  If you drop the juggling ball, you must start the cooldown over.

{\bf Ranged:} Ranged weapons are represented by Nerf blasters.  To make an attack, speak the incant and fire the blaster.  There is no cooldown; you may fire as quickly as you can load ammunition.  Darts will be limited.  You may recover darts that you fire, but not those fired by NPCs, which should be a different color.

{\bf Magic:}  Magic attacks are represented by spellpackets.  All spells have an associated ritual, which involves speaking a given phrase.  Once you do so, you may immediately throw a spellpacket with the indicated incant.  You may not prepare a spell: if you pause for at least 5 seconds between words or for at least 5 seconds before throwing the spellpacket, the spell fizzles and you must start the spell again.  If you misspeak during the ritual, you must start over the from the beginning.

\section{Incant Effects}

Certain attacks may have incants that cause them to do things other than direct damage.  If an incant contains any of the following phrases, the attack is modified as indicated.

{\bf Blast:} This attack effects everyone within 1 ZoC of where the attack lands.

{\bf Fire:} The attack deals fire damage.  The attack ignores DR, but can be negated by fire immunity.

{\bf Lightning:} The attack deals lightning damage.  The attack ignores DR, but can be negated by lightning immunity.

{\bf Piercing:} The attack ignores DR.  Piercing attacks may also ignore other defensive abilities.


\section{Status Effects}

The following status effects and attack modifiers exist in game.  If you are hit by an attack that uses one of these incants, take the appropriate effect.  Unless indicated otherwise, status effects will last for {\bf 30 seconds}.

{\bf Daze:} You may walk no faster than heel-toe.  You may not activate any mechanics, perform any attacks, or cast any spells.

%{\bf Disarm:} You may not perform any attacks.

{\bf Haste:} You may skip the cooldown on your next next melee or thrown attack.  After you do so, the {\bf haste} ends.

{\bf Immobilized:}  While immobilized, you may not move or perform any actions.  {\bf Immobilization} is only triggered by environmental effects and will only wear off when the mechanic indicates.

{\bf Silence:} You may not speak in-game, either to communicate with your party or to speak the ritual component of a spell.  You may still use abilities that require incants or that use an $n$-count.

{\bf Poison:}  Every minute, you will take one point of damage as directed to by the GM.  The poison will wear off after it has caused damage three times.

{\bf Root:} When you are rooted, pick one of your  limbs in contact with the ground.  You may not move that limb.

\section{Other Abilities}


% Starting characters

% Combat

% Attack Types

%LIGHT



\end{document}
