\documentclass[green]{grimrock}
\begin{document}
\name{\gRules{}}

\section{Scenario}

A dungeon entrance lies at the top of Mount Grimrock, inaccessible except by airship.  Prisoners committing egregious crimes against the crown are sentenced to be thrown into the dungeon of Grimrock and abandoned there.  Any who pass through the dungeon and return are pardoned for their crimes, but no one has ever returned.

You and three other criminals have been chained together and banished into the dungeons of Grimrock.


\section{Chain}

All of the players are chained together. The manacles and chain will be represented by clipping players onto a loop of rope.  In principle the characters are manacled together and cannot free themselves from the rope, but in practice players may need to detach for safety reasons or to rearrange the party.

If any player is detached from the chain, all players attached to the chain are {\bf rooted}.  Any players unattached are {\bf dazed} and may only walk towards the chain.

If you somehow find a way to gain a tactical advantage by detaching some of your players from the chain anyway, the GMs will find a way to make sure that it doesn't help either.

\section{Dungeon Components}

{\bf Pits:}  Large pits are represented by red masking tape on the floor.  If any part of your body touches the interior of a pit, you trip into it, but are caught by your teammates.  You take 1 piercing damage, and are {\bf immobile} until you escape the pit, which may only be done with the assistance of a teammate.  Pulling an ally out of a pit is a 15-count, during which time you are {\bf immobile}. If the entire party somehow manages to fall into a pit simultaneously, they call all climb out on a 15-count. When leaving a pit, you must exit on the same side that you fell in on.

{\bf Strings:} Strings represent hazardous materials.  If you touch a string, take 1 piercing damage immediately.  There may be additional effects controlled by a GM.

{\bf Pressure Plates:} Pressure plates are represented by blue masking tape on the floor.  These plates may vary in sensitivity.

{\bf Buttons:} Buttons on the wall are represented by small signs.

{\bf Stairs:} Stairs may not be transversed unless explicitly indicated otherwise.

{\bf Crystal of Life:}  Between very floor is a Crystal of Life which will heal players fully, remove status effects, revive {\bf downed} characters, save the party progress, and grant each player a new {\bf talent}.

\section{Light}

Dungeons are dark and you will need a source of light to allow you to escape.  You have a torch, but it will only last so long.

Torches are physrepped by foam rods.  To use torches to illuminate, one player must hold it above their head at all times.  If the torch is lowered, set down, or dropped, the dungeon is cast into darkness: until they have a source of light, players may only walk heel-toe.

Once lit, a torch will remain lit for only 25 minutes, as timed by a GM.  If your last torch is exhausted, the game will end and your party will be lost in the dungeon forever.

\section{Talents}

Characters will accumulate {\bf talents} over the course of the game.  These represent additional abilities that the player will gain access to.  See the appropriate greensheet for more information.  No player may take the same talent twice.

Additionally, at the start of game you will be allowed to choose from one of a number of character templates which will determine your maximum hit points, and may give you some starting talents.

\section{Combat}

Combat will be represented by player skill in dodging physreps.  All attacks have an incant associated with them that describes the effects, usually including an amount of damage, any possibly status effects or attack modifiers.  When you perform the attack speak the incant clearly.  If you are hit by the attack --- the attacker calls the shot in case of a tie --- take the corresponding effect.  For example, an attack with an incant "Silence 2" would cause 2 damage and inflict {\bf Silence}.  If you have DR, reduce the damage taken by that amount.

Beyond physically avoiding the physrep, certain attacks may be resisted or dodged.  If an attack fails to penetrate your DR or you are immune to the attack, incant ``resist''.  If you have an ability that allows you to {\bf dodge} the attack, incant ``dodge''.  In generally, {\bf dodges} are a limited-use ability.

\subsection{Damage}  All players and monsters have an HP stat that indicates your current health and a maximum HP stat which indicates their maximum health.  At the start of the game and between each floor, your HP will be restored to its maximum.

If you take damage, decrease your HP by the corresponding amount.  If your HP decreases to 0 or decreases below 0, you are {\bf disabled}.  While {\bf disabled}, you may move no faster than heal-toe and may not perform any attacks.  You may interact with other mechanics, including consuming healing potions, which can restore you to health if they bring you above 0 HP.

\subsection{Attacks}

Different attacks are represented in different ways.  Most attacks have a cooldown ritual, which is performed before the implementing the attack, although for physical attacks these rituals can be done in advance. Note that unless you know otherwise, you may store up progress for a cooldown ritual for as long as desired, though starting a second cooldown ritual negates a progress made on the first one. You character will generally have access only to attacks granted to them by items in their possession that they meet the prerequisites for using.

{\bf Melee:} Melee attacks are usable while holding a melee weapon and the attack is physrepped by a ping-pong ball.  Throw the ball and speak the incant.  You must perform a cooldown ritual before performing an attack.  To do so \TODO{Figure out melee cooldown}. Additionally, any character may make a melee attack with their fists will cooldown 7 and incant ``1 damage''.

{\bf Thrown:}  Thrown weapons are indicated by juggling balls.  To perform a thrown attack, throw the ball \emph{underhanded}.  Thrown attacks have a cooldown ritual.  To perform the ritual, throw the juggling ball in the air and catch it a number of times equal to the cooldown number.  The ball must be thrown at least three feet in the air, and caught at or below the height it was thrown.  If you drop the juggling ball, you must start the cooldown over.

{\bf Ranged:} Ranged weapons are represented by Nerf blasters.  To make an attack, speak the incant and fire the blaster.  There is no cooldown; you may fire as quickly as you can load ammunition.  Darts will be limited.  You may recover darts that you fire, but not those fired by NPCs, which should be a different color.

{\bf Magic:}  Magic attacks are represented by spellpackets.  All spells have an associated ritual, which involves speaking a given phrase.  Once you do so, you may immediately throw a spellpacket with the indicated incant.  You may not prepare a spell: if you pause for at least 5 seconds between words or for at least 5 seconds before throwing the spellpacket, the spell fizzles and you must start the spell again.  If you misspeak during the ritual, you must start over the from the beginning.

\section{Incant Effects}

Attacks in game have many possible effects. This effect of a given attack is distinguished by the incant made upon making the attack. If you are hit by an attack and did not hear the incant, say ``miscast'' (or something else appropriate) to indicate this so that the effect may be restated. An incant will consist of several effects or modifiers as listed below:

{\bf $n$-Damage:} The attack does a total of $n$ damage to anyone that it hits.

{\bf Blast:} This attack effects everyone within 1 ZoC of where the attack lands.

{\bf Fire:} The attack deals fire damage.  The attack ignores DR, but can be negated by fire immunity.

{\bf Lightning:} The attack deals lightning damage.  The attack ignores DR, but can be negated by lightning immunity.

{\bf Piercing:} The attack ignores DR.  Piercing attacks may also ignore other defensive abilities.

{\bf Push:} The target of an attack with the push incant must take three reasonable sized steps away from the attacker or until they run into an in-game wall or out-of-game obstacle. If the target was rooted (see below) when they were hit, they should un-root to take these steps and then re-root afterwards.

{\bf Pull:} The target of an attack with the push incant must take three reasonable sized steps towards the attacker or until they run into an in-game wall or out-of-game obstacle. If the target was rooted (see below) when they were hit, they should un-root to take these steps and then re-root afterwards.


\subsection{Status Effects}

The following status effects and attack modifiers exist in game.  If you are hit by an attack that uses one of these incants, take the appropriate effect.  Unless indicated otherwise, status effects will last for {\bf 30 seconds}.

{\bf Daze:} You may walk no faster than heel-toe.  You may not activate any mechanics, perform any attacks, or cast any spells.

%{\bf Disarm:} You may not perform any attacks.

{\bf Haste:} You may skip the cooldown on your next next melee or thrown attack.  After you do so, the {\bf haste} ends.

{\bf Immobilized:}  While immobilized, you may not move or perform any actions.  {\bf Immobilization} is only triggered by environmental effects and will only wear off when the mechanic indicates.

{\bf Silence:} You may not speak in-game, either to communicate with your party or to speak the ritual component of a spell.  You may still use abilities that require incants or that use an $n$-count.

{\bf Poison:}  Every minute, you will take one point of damage as directed to by the GM.  The poison will wear off after it has caused damage three times.

{\bf Root:} When you are rooted, pick one of your  limbs in contact with the ground.  You may not move that limb.

{\bf Slow:} While you are slowed, you must perform the ritual for any attack twice consecutively before making the attack. Furthermore, while slowed you can only walk heel-toe.

\section{Other Abilities}

Certain abilities may grant other effects.  The common effects are compiled below.

{\bf Damage Reduction (DR):} {\bf DR} comes attached with a number, which reduces the damage you take from all physical sources (not fire, lightning, or piercing) by that number.

{\bf Enchant:} If you gain {\bf enchant}, the next melee, thrown, or ranged attack you make deals 2 additional damage.

{\bf Dodge:} If you gain {\bf dodge}, you may ignore the effects of the next attack that hits you.  If you do so, incant ``dodge''.
% Starting characters

% Combat

% Attack Types

%LIGHT



\end{document}
