\documentclass[green]{grimrock}
\begin{document}
\name{\gNPC{}}

{\bf [Greater] Dire Rat}

Headband Color: Pink [and Black]

Hit Points: 5[7]

Cooldown: $n$ Squeaks (Make squeaking noise about 1 second apart, last one should be a hiss, make attack one second later)

Attacks: 
\begin{itemize}
\item Ping-pong ball, Incant ``1[2] damage'', Cooldown 4[6]
\end{itemize}

Notes: Remain rooted after hiss in incant.

\medskip

{\bf [Greater] Giant Spider}

Headband Color: Purple [and Black]

Hit Points: 4[8]

Cooldown: Twirl nerf gun around finger $n$ times. (no faster than once a second or so)

Attacks: 
\begin{itemize}
\item Nerf, Incant ``Poison'' Cooldown 6
\item Nerf, Incant ``1 damage'' Cooldown 4
\item [Nerf, Incant ``Root'', Cooldown 6]
\end{itemize}

Notes: Be clear about where you are aiming about a second before firing and do not readjust aim afterwards. Immune to pits.

\medskip

{\bf Turret}

Headband Color: Light Blue

Other stuff: Varies

\medskip

{\bf [Greater] Skeleton Archer}

Headband Color: Red [and Black]

Hit Points: 6[10]

Cooldown: Load, Cock, Aim nerf gun about $n$ seconds per operation.

Attacks:
\begin{itemize}
\item Nerf, Incant ``Fire, 1 damage'', cooldown 1
\item [Nerf, Incant ``Fire, 1 damage, Blast'', cooldown 2]
\end{itemize}

Notes: Remain aiming in the same direction for about 1 second before firing. Fire immunity.

\medskip

{\bf [Greater] Skeleton Swordsman}

Headband Color: Red [and Black]

Hit Points: 12[18]

Cooldown: Brandish foam boffer $n$ times (about 1 second per time)

Attacks:
\begin{itemize}
\item Ping-pong ball, ``1[2] damage'', Cooldown 6[9]
\end{itemize}

Notes: Fire immunity.

\medskip

{\bf Crappy Skeleton Archer}

Headband Color: Red

Hit Points: 3

Cooldown: Load, Cock, Aim nerf gun about $n$ seconds per operation.

Attacks:
\begin{itemize}
\item Nerf, Incant ``1 damage'', cooldown 2
\end{itemize}

Notes: Remain aiming in the same direction for about 1 second before firing. Cannot walk faster than heel-toe. Follow players if in line of sight. Remain stationary if players are not in view.

\medskip

{\bf Ooze [Greater] }

Headband Color: Green [and Black]

Hit Points: 6[9]

Cooldown: Wait $n$ seconds.

Attacks:
\begin{itemize}
\item Ping-pong ball, Incant ``Slow'', Cooldown 10[7]
\item Ping-pong ball, Incant ``Root'', Cooldown 7[5]
\item Ping-pong ball, Incant ``Poison'', Cooldown 5[4]
\item [Ping-pong ball, Incant ``Interrupt'', Cooldown 5]
\end{itemize}

Notes: Cannot move faster than walking speed. Don't be too clever.

\medskip

{\bf [Greater] Giant Snail}

Headband Color: [and Black]

Hit Points: 20 DR 1[2]

Cooldown: Head bob (about once per second)

Attacks:
\begin{itemize}
\item Ping-pong Ball, Incant ``1[2] damage'', Cooldown 6
\end{itemize}

Notes: Can only walk heel-toe.

\medskip

{\bf [Greater] Beholder }

Headband Color: Yellow [and Black]

Hit Points: 9[12]

Cooldown: Blinky motions with hands (about 1 per second)

Attacks:
\begin{itemize}
\item Spellpacket, Incant: ``Lightning, 2 damage'', Cooldown 6
\item Spellpacket, Incant: ``Lightning, 1 damage'', Cooldown 15[10] (can make 4 attacks in a row)
\item [Spellpacket, Incant: ``Interrupt, Blast'', Can make for free immediately after being hit with any attack (does not reset your cooldowns)]
\end{itemize}

Notes: Immune to pits, Immune to lightning, Feel free to be smart about things.

\medskip

{\bf Mindflayer}

Headband Color: Cat and Black

Hit Points: 50

Cooldown: Wait $n$ seconds between attacks

Attacks:
\begin{itemize}
\item Spellpacket, Incant ``Silence, Blast'', Cooldown 0 (only while shield is up and if PCs are talking back to him)
\item Spellpacket, Incant ``1 Damage'', Cooldown 1 (if resisted can then make next attack for 2 damage)
\item Spellpacket, Incant ``1 Damage, Blast'', Cooldown 2 (can only target self)
\item Spellpacket, Incant ``Interrupt'', Cooldown 1 (only at fewer than 20 hit points)
\end{itemize}

Notes: Immune to push/pull. Follows PCs at walking speed in the most direct manner. Has shield. Resists all effects while shield is up, but cannot attack (except for silence attack above). While shield is up, can summon greater monsters at least 1 minute apart when NPCs are available. There are three shield points. They are destroyed the first time any of the following happen:
\begin{itemize}
\item The boss is hit with the magic sword.
\item The bridge is blown up beneath the boss.
\item The boss is caught in the crushing walls trap.
\item The bass is caught in the falling block trap.
\end{itemize}

\end{document}
